Resilience and Home-Space for WSTS \thanks{This work was partly done while the author was supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-08-31 final.tex
section

%\"Ozkan
\alain{pourquoi ne pas juste écrire Proposition 1 \cite{DBLP:conf/gg/Ozkan22}et enlever "notre" proposition 3 ?}
\begin{proposition}[Proposition 1 in \cite{DBLP:conf/gg/Ozkan22}]\label{post*}
For finite-branching WSTS, a basis of $\uparrow \post^*(s)$ is computable for every state $s$ iff the downward-reachability problem is decidable.
\end{proposition}

@@

\noindent
\textbf{Proposition~\ref{liveness reset}}
{\em In reset Petri nets, the zero reachability problem can be reduced to {\sc $t$-liveness}.}

>>>>

%\"Ozkan
%\alain{pourquoi ne pas juste écrire Proposition 1 \cite{DBLP:conf/gg/Ozkan22}et enlever "notre" proposition 3 ?}
\begin{proposition}[Proposition 1 in \cite{DBLP:conf/gg/Ozkan22}]\label{post*}
For finite-branching WSTS, a basis of $\uparrow \post^*(s)$ is computable for every state $s$ iff the downward-reachability problem is decidable.
\end{proposition}

@@

\noindent
\textbf{Proposition~\ref{liveness reset}}
{\em In reset Petri nets, the zero reachability problem can be reduced to {\sc $t$-liveness}.}\\

We deduce that:\\
